\documentclass{article}
%\usepackage{fullpage}

\oddsidemargin -.125in
\evensidemargin 1.0in
\textwidth 6.5in
\headheight 0.0in
\topmargin -.6in
\textheight 10.5in

\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\begin{document}

\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
{\large \textbf{Joseph F. Miklojcik III}}  & \\
56 Freemont Court  & 732-754-1003 \\
Somerset, NJ, 08873 & jfm3@jfm3.org \\
\end{tabular*}

\vspace{0.2in}

%{\large \textbf{Objective}}
%
%To lead a team of rebellious misfit programmers through a series of
%zany yet heartwarming adventures, culminating in surprising victories
%that remind us all of life's rich pageant.
%\vspace{0.2in}

{\large \textbf{Employment}}
\vspace{0.1in}
  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{Senior System Administrator} & April 2009 - Present \\
    Shopwiki Inc. & New York City, NY \\
  \end{tabular*}
  \begin{itemize}
    \item Supported entire infrastructure from crawling to user facing
      applications (Java, C++, Python) on ~200 machines in two data
      centers.  Analyzed, monitored, and improved performance,
      availability, and capacity.
    \item Ran Terabyte scale MySQL, MongoDB, and file systems in
      various software and hardware RAIDs (\texttt{ext3},
      \texttt{ext4}, \texttt{mod\_md}, 3ware/LSI).
    \item Automated installation infrastructure (Anaconda, Kickstart)
      and monitoring infrastructure (Nagios, Munin).  Maintained
      in-house monitoring system (Java).
    \item Configuration and maintenance of load balancer (ZXTM),
      geo-located DNS (UltraDNS), external site testing (Websitepulse).
    \item Managed Amazon EC2 instances, AMIs, EBS volumes, and S3
      storage.  Implemented backups and archives for ~5TB of MongoDB
      and MySQL to Amazon S3 storage.
  \end{itemize}

  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{Owner and General Manager} & May 2006 - Present \\
    Nectarine City LLC & Somerset, NJ \\
  \end{tabular*}
  \begin{itemize}
    \item Provided hundreds of billable hours of FOSS IT consulting
      services and reports at hourly rates.
    \item Wrote ``Nectarine City Handbook of C Programming Style.''
    \item Everything else.
  \end{itemize}

  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{Senior Software Engineer} & September 2006 - April 2009 \\
    WINLAB, Rutgers University & North Brunswick, NJ \\
  \end{tabular*}
  \begin{itemize}
    \item Maintained ORBIT (\texttt{orbit-lab.org}), a 400 node grid
      of computers running Linux (2.6.x, netfilter, frisbee), used for
      performing wireless network research.
    \item Maintained NodeHandler/NodeAgent; RESTful web services for
      operating the ORBIT grid (Ruby 1.8, SBCL 1.x, MySQL 5.x,
      PostgreSQL 8.x).  ORBIT software installs 400 nodes with full
      Linux application stacks in under 8 minutes, and provides a
      RESTful control framework for managing highly distributed
      experiment software.
    \item Virtualized experiment control infrastructure (Xen 3.x),
      including mechanisms for collecting GB of experiment data from
      the 400 node grid.
    \item Wrote firmware for second generation node hardware control
      (C99, uIP, ARM, GCC 4).
    \item Wrote graphic console for visualizing real time experiment
      results from USRP software-defined radio devices (C99, UDP).
    \item Provided basic computing infrastructure for WINLAB,
      including email, web, file, and print services (Ubuntu 7, 8),
      Trac (9.x, 10.x), and an openMosix cluster.
  \end{itemize}

  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{System Programmer} & November 1997 - September 2006 \\
    Rutgers University & Piscataway, NJ \\
  \end{tabular*}
  \begin{itemize}
  \item Led team of eight student system programmers to maintain 700+
    package repository at \texttt{rpm.rutgers.edu}.  Ported this
    packaged software to Solaris 7, 8, and 9.  Made significant
    improvements to several Open Source projects, including OpenLDAP,
    YUM, and FAI.  Maintained in-house PAM modules (Python, C).
  \item Mentored other system administrators at University.
  \item Consulted for thousands of hours throughout the University's
    hundreds of departments; everything from multi-year plans with
    \${}300K budgets to amateur psychotherapy and pulling cable.
    Departments ranged from Libraries to Medical Research
    labs. (Solaris 7, 8, 9, NFS, RHEL 3, Debian 2.x, netfilter, Perl
    5.x, PHP 3.x, Postfix, OpenLDAP, OpenSSL, OpenSSH)
  \item Designed and implemented automated system administration tools
    for Solaris systems (\texttt{cfengine}, RPM, APT, NAGIOS,
    JumpStart, Kickstart, SystemImager).  These tools allowed four
    full time system administrators to run between 100 and 200 servers
    for ~70,000 users.
  \item Administrated Solaris systems for Administrative Services
    (Solaris 7, Oracle 7x, 8x, ADSM, DiskSuite).  Supported two DBAs
    and four Developers in traditional SA role on systems with tens of
    thousands of users, meant to migrate away from a Mainframe.
    Devised disaster recovery plan.  Passed University audits at
    record levels, and wrote ``best practices'' documents.
  \end{itemize}

  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{Software Engineer and Technical Writer} & May 1995 - October 1997 \\
    Pipeline Associates & Parsippany, NJ \\
  \end{tabular*}
  \begin{itemize}
  \item Wrote \texttt{setpagedevice} paper handling code for
    Powerpage, a Postscript interpreter (K\&R C, C90, Postscript
    L2/L3).
  \item Ported Powerpage to four different compiler/hardware
    platforms.  Worked with QA group to ensure port correctness.
  \item Consulted for Pipeline customers, integrating Powerpage into
    seven distinct printers.  Worked closely with customer engineering
    teams.
  \item Wrote three engineering manuals for the Powerpage line of
    products; an Integration Guide, a Programming Style Guide, and a
    detailed Product Overview.  These were used both by customers and
    as marketing material.
  \item Wrote scripts for automated regression tests, working closely
    with QA department (PostScript, bash, C).  Developed and
    documented strategies for best use of Genoa PostScript test suite
    results (PostScript, bash, C).
  \end{itemize}

  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{Member of Technical Staff} & August 1988 - August 1994 \\
    Unipress Software & Edison, NJ \\
  \end{tabular*}
  \begin{itemize}
  \item Maintained Unipress Emacs, Cmacs, and Adamacs (K\&R C, MLisp).
  \item Wrote a portable extension language interpreter close to R3RS
    Scheme, including an efficient garbage collector (K\&R C) and
    non-blocking I/O facilities.
  \item Ported over five software products between Solaris, HPUX, AIX,
    IRIX, and many other versions of UNIX during the early UNIX
    Workstation craze.  Made C/C++ developer kits for UNIX
    workstations, including correctly built X11 and OSF/Motif
    libraries (K\&R C, POSIX.x).
  \item Evaluated tens of software products as Unipress considered
    buying the rights to resell them.  Worked closely with
    business/marketing teams.
  \item Wrote an instrumented C Compiler, which generated self-testing
    object code. (K\&R C, various parser generators).
  \item Editor of \textit{Unipress Emacs User Guide} and
    \textit{Unipress Emacs Reference Manual}, over 1000 pages of
    documentation.  Authored regular Unipress Technical Bulletins,
    reference cards, release notes, and per-version install
    instructions. (Framemaker 3.0, 4.0)
  \end{itemize}
\vspace*{0.2in}
{\large \textbf{Education}}
\vspace*{0.1in}
  \begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{Rutgers University} & New Brunswick, NJ \\
    BA with Honors in Computer Science, 2005 & \\
  \end{tabular*}

\vspace*{0.2in}
\begin{center}
\textbf{References available on request.}
\end{center}

\end{document}
